Untrusted B2B Collaboration using the Blockchain

### 2018-07-18 paper/paper.tex
Restructuring

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%
\author{Jonas Beyer \and Philipp Otto \and S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
	Hasso-Plattner-Institut, Potsdam, Germany\\
	\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
	Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
	Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
	As a result, it is possible to form consensus in the communication between otherwise untrusting parties.
	In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
	We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.

@@

@@

\subsection{Decentralization}
% Decentralized contracts vs. central monitor
% Engine on chain vs. message channel

\section{Architecture}

@@

See appendix for example % TODO

@@

\section{Conclusion}

\section{Appendix}
% TODO highlight different parts as described in section Implementation? or remove?
\begin{lstlisting}[
  caption=Example source code of the Bulk Buyer's factory contract,
  language=Solidity,
  basicstyle=\small,
  xleftmargin=-3cm,
  xrightmargin=-3cm]
pragma solidity ^0.4.24;

contract Manufacturer {
    function receiveOrder(address) public;
    function setBulkBuyer(address) public;
}

contract ManufacturerFactory {
    function createInstance(uint) public returns(address);
    function getAccessAddress() public returns(address);
    function isInstance(uint, address) public view returns(bool);
}

contract Access {
    function isAuthorized(address, string) public returns(bool);
}

contract BulkBuyer {
    event ProductReceived();
    event StartOfProductionReceived();
    event Selfdestructed();

    address _factory;
    Access _localAccess;
    uint _id;

    ManufacturerFactory _manufacturerFactory;
    Access _manufacturerAccess;
    Manufacturer _manufacturer;

    modifier manufacturerAuthorized(address sender, string taskName) {
        require(_manufacturerFactory.isInstance(_id, msg.sender));
        require(_manufacturerAccess.isAuthorized(sender, taskName));
        _;
    }

    modifier localAuthorized(string taskName) {
        require(_localAccess.isAuthorized(msg.sender, taskName));
        _;
    }

    constructor(
        address localAccess,
        uint counter,
        address manufacturerFactory, address manufacturerAccess, address manufacturerInstance
    ) public {
        _factory = msg.sender;
        _localAccess = Access(localAccess);
        _id = counter;

        _manufacturerFactory = ManufacturerFactory(manufacturerFactory);
        _manufacturerAccess = Access(manufacturerAccess);
        _manufacturer = Manufacturer(manufacturerInstance);
    }

    function placeOrder() public localAuthorized("receiveOrder") {
        _manufacturer.receiveOrder(msg.sender);
    }

    function receiveStartOfProduction(address sender) 
      public manufacturerAuthorized(sender, "receiveStartOfProduction")
    {
        emit StartOfProductionReceived();
    }

    function receiveProduct(address sender) 
      public manufacturerAuthorized(sender, "receiveProduct")
    {
        emit ProductReceived();
        emit Selfdestructed();
        selfdestruct(_factory);
    }
}

contract BulkBuyerFactory {
    event BulkBuyerInstanceCreated(address instanceAddress);

    address _accessAddress;
    uint _counter;

    address _manufacturerAddress = address(0);

    mapping(uint => address) _instances;

    modifier initialized {
        require(_manufacturerAddress != address(0));
        _;
    }

    constructor(address accessAddress) public {
        _accessAddress = accessAddress;
        _counter = 0;
    }

    function setManufacturer(address manufacturerAddress) public {
        _manufacturerAddress = manufacturerAddress;
    }

    function createInstance() public initialized returns(address) {
        _counter = _counter + 1;

        ManufacturerFactory manufacturerFactory = ManufacturerFactory(_manufacturerAddress);
        address manufacturerAccess = manufacturerFactory.getAccessAddress();
        address manufacturerInstance = manufacturerFactory.createInstance(_counter);

        BulkBuyer b = new BulkBuyer(
            _accessAddress,
            _counter,
            manufacturerFactory, manufacturerAccess, manufacturerInstance
        );
        _instances[_counter] = address(b);
        emit BulkBuyerInstanceCreated(b);
        return b;        
    }

    function getAccessAddress() public view returns(address) {
        return _accessAddress;
    }

    function isInstance(uint id, address instanceAddress) public view returns(bool) {
        return _instances[id] == instanceAddress;
    }
}
\end{lstlisting}

>>>>

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%
\author{Jonas Beyer \and Philipp Otto \and S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
%
\institute{
	Hasso-Plattner-Institut, Potsdam, Germany\\
	\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
	Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
	Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
	As a result, it is possible to form consensus in the communication between otherwise untrusting parties.
	In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
	We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.

@@

% Decentralized contracts vs. central monitor
% Engine on chain vs. message channel

@@

@@

See github repo for example % TODO

@@

% future work: 
% - access contract
% - instantiation
% - automatic generation -> template
\section{Conclusion}
